Multisensor Architecture for an Intersection Management System

### 2015-03-25 ch2-mdf_ims.tex
Added list of figures and tables. Corrected some typos.
Added paragraph for ims components

\begin{table}[ht!]
\footnotesize
\centering
\begin{tabular}{|c|c|}
\hline
\textbf{Data Problem} & \textbf{Framework} \\
\hline
\multirow{7}{*}{Imperfection} & Probabilistic \\
& Evidential \\
& Fuzzy reasoning \\
& Possibilistic \\
& Rough set theoretic \\
& HYbridization \\
& Random set theoretic \\
\hline
\multirow{2}{*}{Correlation} & Correlation elimination \\
& Correlation presence \\
\hline
\multirow{6}{*}{Inconsistency} & Sensor validation \\
& Stochastic sensor modeling\\
& Prediction \\
& Augmented state framework \\
& Combination rules \\
& Dempsters' rule \\
\hline
\multirow{3}{*}{Disparateness} & Dempster-Shafer theoretic framework \\
& Human-centered data fusion \\
& Hard-soft data fusion \\
\hline
\end{tabular}
\caption{Classification of fusion algorithms based on challeging problems in data}
\label{fusionAlgClasKhaleghi}
\end{table}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.2125]{fig/2/ims_graph2.png}
\caption{Components of an interesection management system application.}
\label{fusionAlgs}
\end{figure}

Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications as traffic analysis, counting and classification of vehicles or pedestrians, events and incident detection, accidents prevention and security and surveillance applications.

To complete these tasks, many approaches have been proposed for information capture stage, both taking data from vehicle or from the infrastructure. For example, monitoring mobile wireless network like Bluetooth \cite{Friesen2013}, detecting vehicle presence using inductive loops or RFID tags, identifying vehicles and pedestrian using cameras \cite{Buch2011, Strigel2013}, single or multiple laser-scanners \cite{Meissner2010, Meissner2012, Zhao2006, Zhao2008, Zhao2012}, and multi-sensor integrated systems \cite{Meissner2013, Meissner2013a, Meissner2014, GoldHammer2012, Zhao2009}.

>>>>

\begin{table}[ht!]
\footnotesize
\centering
\begin{tabular}{|c|c|}
\hline
\textbf{Data Problem} & \textbf{Framework} \\
\hline
\multirow{7}{*}{Imperfection} & Probabilistic \\
& Evidential \\
& Fuzzy reasoning \\
& Possibilistic \\
& Rough set theoretic \\
& Hybridization \\
& Random set theoretic \\
\hline
\multirow{2}{*}{Correlation} & Correlation elimination \\
& Correlation presence \\
\hline
\multirow{6}{*}{Inconsistency} & Sensor validation \\
& Stochastic sensor modeling\\
& Prediction \\
& Augmented state framework \\
& Combination rules \\
& Dempsters' rule \\
\hline
\multirow{3}{*}{Disparateness} & Dempster-Shafer theoretic framework \\
& Human-centered data fusion \\
& Hard-soft data fusion \\
\hline
\end{tabular}
\caption{Classification of fusion algorithms based on challeging problems in data}
\label{fusionAlgClasKhaleghi}
\end{table}

@@

Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications like traffic analysis, counting and classification of vehicles or pedestrians, event prediction, incident detection, accidents prevention and security and surveillance systems. Those applications have to take into account some of the elements depicted in figure \ref{arch}, so developments in IMS have a wide range of approachesa and objectives. In order to organise and compare IMS applications, five components have been defined in which applications have their main focus, although mutiple components could be involved in the same development. In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them.

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.2125]{fig/2/ims_graph2.png}
\caption{Components of an Intersection Management System application.}
\label{imsComps}
\end{figure}

many approaches have been proposed for information capture stage, both taking data from vehicle or from the infrastructure. For example, monitoring mobile wireless network like Bluetooth \cite{Friesen2013}, detecting vehicle presence using inductive loops or RFID tags, identifying vehicles and pedestrian using cameras \cite{Buch2011, Strigel2013}, single or multiple laser-scanners \cite{Meissner2010, Meissner2012, Zhao2006, Zhao2008, Zhao2012}, and multi-sensor integrated systems \cite{Meissner2013, Meissner2013a, Meissner2014, GoldHammer2012, Zhao2009}.
